Proposed Solution

### 2017-04-17 OOPSLA17/secs/related.tex
autocommit

>>>>

PCheck~\cite{xu16early} aims to add configuration checking code to the system source code by emulating potential commands and behaviors of the system. 
This emulation is a ``white-box'' approach and requires access to the system's source code.
One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is 
hard to emulate, PCheck cannot automatically generate the corresponding checking code.
Due to the emulation based testing strategy, PCheck's scope is limited to reliability problems caused by misconfiguration parameters. 
In contrast, \app is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
By using a rule learning strategy of examples, \app is able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.
